---
title: "Crimes in the US"
author: "Ameera Attiah, Jana Abuhantash, and Ahmad "
date: "2023-11-18"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Problem Statement

"Analyzing Trends and Determinants of Crime Rates in the United States to Inform Policy and Prevention Strategies"

In recent years, the United States has faced complex challenges related to crime. Understanding the trends, causes, and distribution of crime across different regions is crucial for developing effective policies and prevention strategies. This project aims to analyze various factors influencing crime rates, including economic, social, and environmental variables, to identify key drivers and potential areas for intervention.

## Background

U.S. crime rates have varied, decreasing in the 1990s and rising recently in some areas. These trends differ regionally due to factors like urbanization and economic conditions. Socioeconomic issues, the opioid crisis, and drug trafficking also influence crime rates. Technological advances in law enforcement have transformed crime prevention and investigation. However, public perception of crime, often shaped by media, may not always reflect actual statistics.


## Methods Explored

Considered Methods:
List and briefly describe the methods you considered.

Method Selection:
Discuss why you chose the method/tool you did.

## The Methods/Tools Used

Method/Tool Used:
Describe the chosen method/tool.

Rationale:
Explain the rationale behind your choice.


## Results 

Preliminary Results:
Present your initial findings or data.
```{r}

```

Further Results:
More results or visualizations.
```{r}

```


## Lessons Learned

- Analyzed crime trends to identify patterns and anomalies over time.
- Investigated the influence of poverty, education, and unemployment on crime rates.
- Evaluated the success of different policing strategies in crime reduction.
- Faced challenges in gathering accurate crime data.
- The benefits of integrating insights from various disciplines.

## Future Plans

- Explore specific crime types and demographics in further detail.
- Suggest policy and law enforcement improvements.
- Collaborating with field experts for practical application and validation
- Utilize advanced data analysis techniques.
- Assessing the implications of findings on public policy and crime prevention
